New insights into the Weddell Sea ecosystem applying a quantitative network approach

### 2022-12-28 Manuscript/Manuscript.Rmd
Corrected minor suggestions. Still tidying Intro

<!-- Relevance of studying food webs -->
Food web analysis constitutes an important framework for understanding ecological community structure and for conserving biodiversity through ecosystem management [@Thompson2012]. Although topological food web analysis, which considers only the presence and absence of predator-prey interactions, provides important insights into the structure and functioning of ecological communities [e.g. @Pascual2006; @Kortsch2015; @Marina2018; @Cordone2020; @Rodriguez2022], more information on the nature of the trophic interactions is needed to effectively charaterise ecosystem dynamics and stability [@Kortsch2021, @otherRefs]. This is a fundamental step for providing assemessments on ecosystem vulnerability to environmental pressures and for prioritising management actions. In this regard, quantifying the strength of trohic interactions and species' roles within the network are of paramount importance [@Carrara2015; @Allesina2015; @Nilsson2016; @Cirtwill2018a].

<!-- Paragraph on unweighted and weighted networks here? -->
We should maybe write a paragraph about weighted and unweighted approaches here, where we aslo introduce the approach we used...

<!-- Insights of network science to polar ecosystems -->
> [susanne] I moved the paragraph below. it makes more sense to first talk about polar regions in genaral and then introduce the Weddell Sea.
> 
Using a network approach, different types (e.g., terrestial, lake, etc.) of food webs from various geographic locations are studied worldwide, including marine polar food webs [@Carscallen2012; @Santana2013; @Kortsch2019; @Pecuchet2022]. Some of these studies from the Arctic show how food web properties (e.g., connectance) are constrained by environmental factors such as sea ice cover and seawater temperature [@Kortsch2019; @Pecuchet2022]. In the Southern Ocean, important insights have been gained into mechanisms of energy flow, the relative importance and traits of individual species and the influence of environmental variables (e.g., sea-ice) on the structure of local food webs [@Cordone2020; @Rossi2019].
> [susanne] what do you mean here: the relative importance and traits of individual species? What important mechanisms? Can we be more specefic? Can we also be more specific about how environmental variables (e.g., sea-ice) influence the structure of local food webs in the SO?

<!-- Climate change in Weddell Sea -->
The Weddell Sea is expected to be one of the last regions of the Southern Ocean to experience the consequences of climate change due to its extensive ice cover and ocean currents [@Teschke2021] resulting in less sea surface warming compared to other areas of the Southern Ocean. Because of these environmental characteristics, the Weddell Sea may serve as a refuge for Antarctic species which depend on sea ice (e.g. krill, emperor penguin, Weddell seal) or have low heat tolerance (e.g., most notothenioid fishes) due to their adaptations to freezing tempeartures [@Griffiths2017]. While essential large-scale hydrodynamic relationships are relatively well-known for this region [@deSteur2019], information on the current distribution, abundance and sensitivity to climate change is only partially known for a few species (e.g., XXXXX) [@Houstin2022].
> [susanne]it is not clear from the text why Weddell Sea is one of the last regions of the SO to face the consequences of warming, be explicit here, how are the currents affecting the Weddell Sea?
>

<!-- Food web studies about Weddell Sea / Key species or species role -->
Overall, the complexity the Weddell Sea food web is high and consists of 488 species and 16200 predator-prey interactions[@Jacob2011]. In an attempt to better understand species role related to food web stability, Jacob et al. (2011) performed secondary extinction experiments and found that the removal of small to medium-sized, and not large, organisms caused a cascade of secondary extinctions. This findings highlighted the relative importance of predators, rather than prey, in the architecture, functioning and stability of the Weddell Sea food web, which coincides with findings from recent meta-analyses in natural complex food webs [@Brose2019; @Perkins2022]. Other investigations have considered this food web though in a meta-analysis context....[more text here, WHAT DO THESE META_ANALSYES STUDIES SHOW] [@Brose2019; @Perkins2022; @Saravia2022].

@@

<!-- Objectives -->
In this study, we aim to go beyond a purely topological (presence/absence) assessment of who eats whom in the Weddell Sea ecosystem by providing a quantitative analysis of the trophic interaction network. We aim to analyse role for the structure and stability of the food web. To achieve this, we: 1) estimated the strength for each interaction in the Weddell Sea food web, 2) characterised species role considering both weighted and unweighted properties, and 3) analysed the species’ role realted to the stability of the food web. This is the first time that the interaction strength was estimated for all the interactions mostly at the species level for the Weddell sea food web

@@

To analyse the impact of species on food web stability, we performed extinction simulations deleting one species at a time, that is for every extinction network size was reduced by one species only. After each extinction, we calculated the stability of the network minus the targeted species (489 nodes) and compared it with that of the whole network (490 nodes in total). To calculate stability, we used the mean of the real part of the maximum eigenvalue of the Jacobian matrix using randomized Jacobians and keeping the predator-prey sign structure fixed [@Allesina2008; @Grilli2016]. This index indicates a more stable food web when it is negative. We performed 1000 simulations for each species extinction and obtained a mean maximum eigenvalue for each case. At last we statistically analysed such a difference with an Anderson-Darling test considering a p-value < 0.01 [@Scholz1987]. If this difference is positive, then the stability of the food web is higher if a species was removed, and vice versa. A detailed description on the stability calculations can be found in Supplementary Material.

@@

The statistical distribution that best fitted the empirical interaction strength distribution of the Weddell Sea food web was a ‘gamma’ due to the high proportion of weak interactions and the existence of a few strong interactions (Figure 3, Table S3). <!-- Gamma parameters ?? -->

@@

Our analyses show that the distribution of species interaction strength at the network level is asymmetric, i.e., the Weddell Sea food web contains many weak interactions and only a few strong ones. This finding is consistent with many previous theoretical and empirical studies [e.g. @McCann1998; @Neutel2002; @Emmerson2004; @Wootton2005; @Kortsch2021]. The asymmetric distribution of interaction strength in food webs has been interpreted as an explanation for the persistence of complex communities in nature [@Bascompte2005; @Allesina2015; @Nilsson2016]. Here we show that this pattern is also prevalent in the Weddell Sea, one of the most complex food webs to date, comprising 490 species and 16041 predator-prey interactions. This finding is in someway validating the method we used, validation of allometric methods of IS estimation not including interaction dimensionality has been performed for microcosmos of relatively few species [@Jonsson2018]. <!--This finding reinforces the call for the inclusion of IS in food web studies to understand better the ecosystem functioning, and species and whole network responses to environmental perturbations.-->

@@

We employed a range of descriptors using both unweighted and weighted food web properties to characterise the dynamic and multifaceted nature of the Weddell Sea food web. Our results show a positive relationship between interaction strength and trophic level, and between interaction strength and species degree. Mean interaction strength increases with trophic level and species degree. The former relationship contradicts studies that suggest that mid-trophic level species (which, krill??? examples are always good) are involved in the major pathways of energy flow in high-latitude marine ecosystems [@Pinkerton2014; @Murphy2016; @McCormack2020; @Riccialdelli2020]. However, this finding could also be explained by the lack of species biomass information in the calculation of interaction strength using the methodology we applied [@Parwar2012]. The methodlogy by Parwar et al.(2012) allows information on species density/biomass to be included, but this type of data was not available for the majority of  species in our food web. In the Weddell Sea, species with high degree also tend to have high mean interaction strengthsThe positive relationship between interaction strength and species degree reinforces the central role of species with many interactions: species with a high degree (hubs) have a large impact on overall food web structure and functioning [@Dunne2002a; @Kortsch2015]. This information on the quantity and quality of interactions and its relationship enables a robust assessment of the species’ role in the stability of the food web [@Cirtwill2018a].

@@

Only a few species play a key role with respect to the Weddell Sea food web stability, according to the mean maximum eigenvalue stability index employed in this study. This is in concordance with other studies on complex empirical food webs in marine ecosystems in the Arctic and other locations in Antarctica [@Kortsch2015; @Marina2018; @Rodriguez2022]. These key species are characterised by a particular set of food web properties: high to mean IS; mid to high trophic level; a relatively high number of interactions; and mid to low trophic similarity. In a previous study on sequential extinction simulations for the Weddell Sea food web [@CITA!!!], it was found  that larger bodied-sized species could be lost without causing a collapse of the network. A major caveat of this finding, also recognised by the authors, was that population dynamics were ignored and hence no top-down extinctions, or other indirect effects, could occur. In our study we considered such top-down effects by including information on the species IS, which is of paramount importance when analysing the response of perturbations in ecological communities [@McCann1998; @Montoya2009; @Novak2011]. Thus, our study suggests that species with high mean IS and high trophic levels need to be considered with particular attention when trying to predict the effects of perturbations on the Weddell Sea ecosystem. This conclusion is further reinforced by the finding that these species have mid to low trophic similarity, which means that few other species of the food web can occupy the same trophic role. In a review, it was emphasised that polar pelagic communities are particularly sensitive to changes due to a low functional redundancy at key trophic levels [@Murphy2016]. Here we provide broader analyses of species impact on food web robustness by including species from all habitats (benthic, pelagic and land-based). This suggests that the sensitivity of marine polar ecosystems to environmental perturbations is a concern also beyond the pelagic realm.

@@

<!-- LAS Figure 2 is confusing, on the left side the title is "Weighted" but the network seems unweighted, I would delete the small predator-prey on the left, and explain that arrow are the flux of energy thus pointin to the predator, and that IS is represented by the width of the arrow. -->

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web."}
knitr::include_graphics("Fig.2_ToyFoodWeb.jpg")
```

>>>>

<!-- Relevance of studying food webs -->
Food web analysis constitutes an important framework for understanding ecological community structure and for conserving biodiversity through ecosystem management [@Thompson2012]. Although topological food web analysis, which considers only the presence and absence of predator-prey interactions, provides important insights into the structure and functioning of ecological communities [e.g. @Pascual2006; @Kortsch2015; @Marina2018; @Cordone2020; @Rodriguez2022], more information on the nature of the trophic interactions is needed to effectively charaterise ecosystem dynamics and stability [@Kortsch2021, @otherRefs]. This is a fundamental step for providing asseessments on ecosystem vulnerability to environmental pressures and for prioritising management actions. In this regard, quantifying the strength of trohic interactions and species' roles within the network are of paramount importance [@Carrara2015; @Allesina2015; @Nilsson2016; @Cirtwill2018a].

@@

<!-- Paragraph on unweighted and weighted networks here? -->
We should maybe write a paragraph about weighted and unweighted approaches here, where we also introduce the approach we used... 
Need to check Kortsch et al. 201

<!-- Insights of network science to polar ecosystems -->
> [susanne] I moved the paragraph below. it makes more sense to first talk about polar regions in general and then introduce the Weddell Sea. TIM: Agree.

Using a network approach, different types (e.g., terrestial, lake, marine) of food webs from various geographic locations are studied worldwide, including marine polar food webs [@Carscallen2012; @Santana2013; @Kortsch2019; @Pecuchet2022]. Some of these studies from the Arctic show how food web properties (e.g., connectance) are constrained by environmental factors such as sea ice cover and seawater temperature [@Kortsch2019; @Pecuchet2022]. In the Southern Ocean, important insights have been gained into mechanisms of energy flow, the relative importance and traits of individual species and the influence of environmental variables on the structure of local food webs [@Cordone2020; @Rossi2019].
> [susanne] what do you mean here: the relative importance and traits of individual species? What important mechanisms? Can we be more specefic? Can we also be more specific about how environmental variables (e.g., sea-ice) influence the structure of local food webs in the SO?
Need to check Rossi2019

<!-- Climate change in Weddell Sea -->
The Weddell Sea is expected to be one of the last regions of the Southern Ocean to experience the consequences of climate change due to its extensive ice cover and ocean currents [@Teschke2021] resulting in less sea surface warming compared to other areas of the Southern Ocean. Because of these environmental characteristics, the Weddell Sea may serve as a refuge for Antarctic species which depend on sea ice (e.g. krill, emperor penguin, Weddell seal) or have low heat tolerance (e.g., most notothenoid fishes) due to their adaptations to freezing temperatures [@Griffiths2017]. While essential large-scale hydrodynamic relationships are relatively well-known for this region [@deSteur2019], information on the current distribution, abundance and sensitivity to climate change is only partially known for a few species (e.g., emperor penguin) [@Houstin2022].
> [susanne]it is not clear from the text why Weddell Sea is one of the last regions of the SO to face the consequences of warming, be explicit here, how are the currents affecting the Weddell Sea?
Need to check Teschke2021

<!-- Food web studies about Weddell Sea / Key species or species role -->
Overall, the complexity the Weddell Sea food web is high and consists of 488 species and 16200 predator-prey interactions[@Jacob2011]. In an attempt to better understand species role related to food web stability, Jacob et al. (2011) performed secondary extinction experiments and found that the removal of small to medium-sized, and not large, organisms caused a cascade of secondary extinctions. These findings highlighted the relative importance of predators, rather than prey, in the architecture, functioning and stability of the Weddell Sea food web, which coincides with findings from recent meta-analyses in natural complex food webs [@Brose2019; @Perkins2022]. Other investigations have considered this food web though in a meta-analysis context....[more text here, WHAT DO THESE META_ANALSYES STUDIES SHOW] [@Brose2019; @Perkins2022; @Saravia2022].

<!-- Objectives -->
In this study, we aim to go beyond a purely topological (presence/absence) assessment of who eats whom in the Weddell Sea ecosystem by providing a quantitative analysis of the trophic interaction network. We aim to analyse the species' role for the structure and stability of the food web. To achieve this, we: 1) estimated the strength for each interaction in the Weddell Sea food web, 2) characterised species role considering both weighted and unweighted properties, and 3) analysed the species’ role related to the stability of the food web. This is the first time that the interaction strength was estimated for all the interactions mostly at the species level for the Weddell sea food web.

@@

To analyse the impact of species on food web stability, we performed extinction simulations deleting one species at a time, that is for every extinction network size was reduced by one species only. After each extinction, we calculated the stability of the network minus the targeted species (489 nodes) and compared it with that of the whole network (490 nodes in total). To calculate stability, we used the mean of the real part of the maximum eigenvalue of the Jacobian matrix using randomized Jacobians and keeping the predator-prey sign structure fixed [@Allesina2008; @Grilli2016]. This stability index indicates a more stable food web when it is negative. We performed 1000 simulations for each species extinction and obtained a mean maximum eigenvalue for each case. At last we statistically analysed such a difference with an Anderson-Darling test considering a p-value < 0.01 [@Scholz1987]. If this difference is positive, then the stability of the food web is higher if a species was removed, and vice versa. A detailed description on the stability calculations can be found in Supplementary Material.

@@

The statistical distribution that best fitted the empirical interaction strength distribution of the Weddell Sea food web was a ‘gamma’ due to the high proportion of weak interactions and the existence of a few strong interactions (Figure 3, Table S3). <!-- Gamma parameters: added in Supplementary Material -->

@@

Our analyses show that the distribution of species interaction strength at the network level is asymmetric, i.e., the Weddell Sea food web contains many weak interactions and only a few strong ones. This finding is consistent with many previous theoretical and empirical studies [e.g. @McCann1998; @Neutel2002; @Emmerson2004; @Wootton2005; @Kortsch2021]. The asymmetric distribution of interaction strength in food webs has been interpreted as an explanation for the persistence of complex communities in nature [@Bascompte2005; @Allesina2015; @Nilsson2016]. Here we show that this pattern is also prevalent in the Weddell Sea, one of the most complex food webs to date, comprising 490 species and 16041 predator-prey interactions. This finding is in someway validating the method we used; validation of allometric methods of IS estimation not including interaction dimensionality has been performed for microcosmos of relatively few species [@Jonsson2018]. <!--This finding reinforces the call for the inclusion of IS in food web studies to understand better the ecosystem functioning, and species and whole network responses to environmental perturbations.-->

@@

We employed a range of descriptors using both unweighted and weighted food web properties to characterise the dynamic and multifaceted nature of the Weddell Sea food web. Our results show a positive relationship between interaction strength and trophic level, and between interaction strength and species degree. Mean interaction strength increases with trophic level and species degree. The former relationship contradicts studies that suggest that mid-trophic level species (e.g. krill, mesopelagic fish, squid) are involved in the major pathways of energy flow in high-latitude marine ecosystems [@Pinkerton2014; @Murphy2016; @McCormack2020; @Riccialdelli2020]. However, this finding could also be explained by the lack of species biomass information in the calculation of interaction strength using the methodology we applied [@Parwar2012]. The methodology by Pawar et al. (2012) allows information on species density/biomass to be included, but this type of data was not available for the majority of  species in our food web. In the Weddell Sea, species with high degree also tend to have high mean interaction strengths. The positive relationship between interaction strength and species degree reinforces the central role of species with many interactions: species with a high degree (hubs) have a large impact on overall food web structure and functioning [@Dunne2002a; @Kortsch2015]. This information on the quantity and quality of interactions and its relationship enables a robust assessment of the species’ role in the stability of the food web [@Cirtwill2018a].

@@

Only a few species play a key role with respect to the Weddell Sea food web stability, according to the mean maximum eigenvalue stability index employed in this study. This is in concordance with other studies on complex empirical food webs in marine ecosystems in the Arctic and other locations in Antarctica [@Kortsch2015; @Marina2018; @Rodriguez2022]. These key species are characterised by a particular set of food web properties: high to mean IS; mid to high trophic level; a relatively high number of interactions; and mid to low trophic similarity. In a previous study on sequential extinction simulations for the Weddell Sea food web [@Jacob2011], it was found  that larger bodied-sized species could be lost without causing a collapse of the network. A major caveat of this finding, also recognised by the authors, was that population dynamics were ignored and hence no top-down extinctions, or other indirect effects, could occur. In our study we considered such top-down effects by including information on the species IS, which is of paramount importance when analysing the response of perturbations in ecological communities [@McCann1998; @Montoya2009; @Novak2011]. Thus, our study suggests that species with high mean IS and high trophic levels need to be considered with particular attention when trying to predict the effects of perturbations on the Weddell Sea ecosystem. This conclusion is further reinforced by the finding that these species have mid to low trophic similarity, which means that few other species of the food web can occupy the same trophic role. In a review, it was emphasised that polar pelagic communities are particularly sensitive to changes due to a low functional redundancy at key trophic levels [@Murphy2016]. Here we provide broader analyses of species impact on food web robustness by including species from all habitats (benthic, pelagic and land-based). This suggests that the sensitivity of marine polar ecosystems to environmental perturbations is a concern also beyond the pelagic realm.

@@

<!-- LAS Figure 2 is confusing, on the left side the title is "Weighted" but the network seems unweighted, I would delete the small predator-prey on the left, and explain that arrow are the flux of energy thus pointin to the predator, and that IS is represented by the width of the arrow. TIM: I corrected it & added the explanation in the caption. -->

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Scheme of a network showing the weighted and unweighted properties we used to characterise the species of the Weddell Sea food web. Directed arrows indicate the flow of energy; the width of the arrow represents the interaction strength of it."}
knitr::include_graphics("Fig.2_ToyFoodWeb.jpg")
```
